### 2020-07-15 code/figure3.Rmd

<div style="text-align: right"> Figure 3 data </div>
```{r group-pathway-enrichment-data-generation, eval=FALSE}
tumor_clusters <- fread("../data/umap_2d_3d_coors.tsv") ## load in data
tumor_clusters <- tumor_clusters %>% as.data.frame() %>% dplyr::select(V1, knn_clust) ## select the relevant columns

@@

```{r group-pathway-enrichment heatmap}
load("../data/effect_heatmap.Rda") ## load data

>>>>

```{r group-pathway-enrichment-data-generation, eval=FALSE}
tumor_clusters <- fread("../data/umap_2d_3d_coors.tsv") ## load in data
tumor_clusters <- tumor_clusters %>% as.data.frame() %>% dplyr::select(V1, knn_clust) ## select the relevant columns

@@

```{r group-pathway-enrichment heatmap, fig.cap="**Figure 3. Pathway-specific enrichment within clusters.** Heatmap shows relative enrichment of each pathway (rows) within each numbered cluster (columns). The annotation at left indicates the Reactome pathway group at the second level (check this)."}
load("../data/effect_heatmap.Rda") ## load data

### 2020-07-15 code/figure4.Rmd

```{r figure-4, message = FALSE}
load("../data/class67_gene_2_path_heatmap.Rda") ## load data
load("../data/path_match_in_set.Rda")

>>>>

```{r figure-4, message = FALSE, fig.cap="**Figure 4: Some genes with multiple pathway memberships drive clustering.** Each column is a tumor in class 6 or 7, each row represents a gene with mutation (red) or not mutated (grey). The genes are organized according to which of the top distinguishing pathways for this class that they effect. Some genes affect multiple pathways, as indicated by the bars at left. The highlighted genes at right are all proteasomal subunits.", eval=FALSE}

load("../data/class67_gene_2_path_heatmap.Rda") ## load data
load("../data/path_match_in_set.Rda")
